MSA Project

### 2022-04-06 MSA Project.Rmd
Added data and references

---
title: "MSA Project"
author: "Niko Miller"
date: "`r format(Sys.time(), '%d.%m.%Y')`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

Lorem Ipsum

>>>>

---
title: "MSA Project"
author: "Niko Miller"
date: "`r format(Sys.time(), '%d.%m.%Y')`"

output: pdf_document

bibliography: references.bib

header-includes:
- \pagenumbering{gobble}

---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

```

\tableofcontents

\newpage
\pagenumbering{arabic}

# Data

I used the package PXWEB API [@pxweb] to retrieve a data set on key ratios for all of Finland's municipalities during 1987-2019 according to the 2020 municipality classification [@data].

@@

\pagebreak
# References
